Title

### 2023-08-17 index.qmd
added time series plot of raw salinity and temp trends

---
title: "Exploratory data analysis"
author: 
   - name: Marcus Beck, <mbeck@tbep.org>
institute: "Tampa Bay Estuary Program"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    css: styles.css
    code-tools: 
      source: https://github.com/tbep-tech/temp-manu/blob/main/index.qmd
execute:
  echo: false
  warning: false
filters:
  - lightbox

>>>>

---
title: "Hot and fresh: Temperature, salinity, and seagrass change in a large Gulf coast estuary"
author: 
   - name: Marcus Beck, <mbeck@tbep.org>
institute: "Tampa Bay Estuary Program"
date: "`r Sys.Date()`"
format:
  html:
    theme: cosmo
    css: styles.css
    code-tools: 
      source: https://github.com/tbep-tech/temp-manu/blob/main/index.qmd
execute:
  echo: false
  warning: false
filters:
  - lightbox

### 2023-08-17 manu-draft.qmd
added time series plot of raw salinity and temp trends

@@

@@

>>>>

Observed trends aggregated by year and bay segment across stations and months in @fig-saltempraw.

@@

For @fig-saltempraw, salinity shows much higher inter-annual variability, but lower intra-year variation among stations. Trends are similar for bottom vs top, temperature shows stronger trend than salinity.

@@

![Long-term salinity and temperature trends for major bay segments from 1975 to 2022. Points are colored by sampling location in the water column.  Points show the average and 95% confidence interval across all stations and sampling months for each year in each bay segment. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay. ](figs/saltempraw.png){#fig-saltempraw}
